InteroceptionStudy_GPValidation

### 2021-08-20 Experiment 2.Rmd
Update Experiment 2.Rmd

Compute proportions outside the sccreen
repixe

@@

```{r}
colnames(X_tmp_df4_full$trackloss)

range(tmp.df2$gaze_x_cor, na.rm = TRUE)

@@

range(tmp.df, na.rm = TRUE)

```
# rezeroing times by trial, by participants

@@

min(tmp.df3$timerezero, na.rm = TRUE)
max(tmp.df3$timerezero, na.rm = TRUE)
natest<-subset(tmp.df3, is.na(tmp.df3$ssid) == TRUE)

@@

Calibration analysis

@@

# fucntion to read all calibration files into one big dataframe
read_cali <- function(flnm) {
  data.table::fread(flnm) %>%
    mutate(filename = flnm)
}

# now read them
db_cali <-
  list.files(pattern = "*.csv",
             full.names = T) %>%
  map_df(~read_cali(.))

# view the dataset
View(db_cali)
unique(db_cali$filename)

# select needed columns
db_cali$ssid <- substring(db_cali$filename, 5,7)
db_cali$valid_points <- sub(".*_", "", db_cali$text)
db_cali$valid_points <- if_else(grepl('valid', db_cali$text), db_cali$valid_points, NULL)
unique(db_cali$valid_points)

db_cali$avg_error <- sub(".*_", "", db_cali$text)
db_cali$avg_error <- if_else(grepl('AvgError', db_cali$text), db_cali$avg_error, NULL)
db_cali$cali_no <- substring(db_cali$text, 23, 24)
db_cali$cali_no <- if_else(grepl('valid', db_cali$text), db_cali$cali_no, NULL)
db_cali$cali_no<- as.numeric(sub("_", "",db_cali$cali_no))

install.packages("useful")

library(useful)
db_cali<- db_cali%>%
  fill(cali_no)%>%
  fill(valid_points)%>%
  fill(avg_error, .direction = 'up')

#find the duplicate rows (some trigger messages were sent twice)
db_cali<- db_cali %>%
  arrange(ssid)%>%
  group_by(ssid)%>%
  mutate(isduplicate = duplicated(avg_error))

db_cali1 <- subset(db_cali, isduplicate == FALSE)

db_cali1 <- select(db_cali1, c(ssid, cali_no, valid_points, avg_error))

# create a order for the calibration
db_cali1$x = row.names(db_cali1)
db_cali1$cali_order <- ave(db_cali1$x,                 # Create numbering variable
                       db_cali1$ssid,
                       FUN = seq_along)
```

# FUNCTION TO CONVERT PIXELS TO DEGREES OF VISUAL ANGLE

@@

pixtoAng<- function(hw,d,r,stimsize){
  #hw - height/width of the monitor(cm) - depending on the axis
  #d - distance of the participant from the monitor (cm)
  #r - vertical/horizontal resolution of the screen (px)
  #stimsize - size of the stimulus on the screen (px)
  deg_per_px = rad2deg(atan2(0.5*hw, d))/(0.5*r)
  visAng <- stimsize * deg_per_px
  return (visAng)
}
#pixtoAng - hw - height/width of the screen in cm - use height for vertical acc/prec, and width for horizontal; d - distance of the participants to the screen (we used an average distance from the logbook); r = height/width of the screen in pixels; stimsize - basically, what you wish to convert from pixels to degrees of visual angle

@@

```{r}
library(ggplot2)

db_cali1$avg_error1<- as.numeric(as.character(db_cali1$avg_error))

db_cali1 %>%
  subset(ssid!= 610)%>%
ggplot(aes(x = cali_order, avg_error1))+
  geom_line(aes(group = ssid))

db_cali1 %>%
  subset(ssid!= 610)%>%
ggplot(aes(x = cali_order, cali_no, color = ssid))+
  geom_line(aes(group = ssid))

db_cali1<- db_cali1%>%
  group_by(ssid)%>%
  mutate(cali_no_resc =  cali_no - lag(cali_no))%>%
  mutate(cali_no_resc = if_else(!is.na(cali_no_resc), cali_no_resc, cali_no))

db_cali1 %>%
  subset(ssid!= 610)%>%
ggplot(aes(x = cali_order, cali_no_resc, colour = ssid))+
  geom_line(aes(group = ssid))

#how many calibrations does it take until accepting
library(lmerTest)

cali_models<- list()
db_cali1$ssid<- as.character(db_cali1$ssid)

db_cali1$cali_order <- as.numeric(as.character(db_cali1$cali_order))
db_cali1$cali_order_z<- scale(db_cali1$cali_order, center = TRUE, scale = TRUE)

cali_models$cali_toaccept<- glmer(cali_no_resc ~ (1| ssid),
                                  family = "poisson", data = db_cali1)

summary(cali_models$cali_toaccept)

summary(glm(cali_no_resc ~ cali_order_z, data = db_cali1))

summary(cali_models$cali_toaccept)

db_cali2<- subset(db_cali1, ssid < 500)
mean(subset(db_cali2, cali_order == 1)$cali_no_resc, na.rm = TRUE)
sd(subset(db_cali2, cali_order == 1)$cali_no_resc, na.rm = TRUE)

# AVG cali
mean(db_cali1$cali_no_resc, na.rm = TRUE)

sd(db_cali1$cali_no_resc)

(mean(db_cali1$avg_error1, na.rm = TRUE)) #43.40358
(median(db_cali1$avg_error1, na.rm = TRUE)) #40.13

install.packages("rCAT")
library(rCAT)

# height and widrh of the sreen in pixes and cm
# H = 32.5 cm (108 Pixels) W = (52)  1920Pix by 1200, distance 63 - 65

pixtoAng(52, 65, 1920, 43.40358) # 0.9849095
pixtoAng(52, 65, 1920, 40.13) # 0.9849095

db_cali1$avg_error1_visang<- pixtoAng(52, 65, 1920, db_cali1$avg_error1)

mean(db_cali1$avg_error1_visang)
sd(db_cali1$avg_error1_visang)
range(db_cali1$avg_error1_visang)

db_cali2_id<- db_cali2%>%
  group_by(ssid)%>%
  summarise_at(c("avg_error"), mean, na.rm = TRUE)

db_cali2$Participant<- db_cali2$ssid

db_cali2_id$avg_error<- NULL
db_cali2$Participant<- NULL

db_cali2<- left_join(db_cali2, db_cali2_id)

db_cali2$Participant<- as.character(db_cali2$Participant)
db_cali2%>%
  ggplot(aes(cali_order, avg_error1))+
  geom_line(aes(group = Participant, colour = Participant))+
  stat_summary(aes(geom = "line"))+
  geom_smooth()

>>>>

Compute proportions outside the screen

@@

```{r eval=FALSE, include=FALSE}
range(tmp.df2$gaze_x_cor, na.rm = TRUE)

@@

range(tmp.df, na.rm = TRUE)
tmp.df2$y_outside<-NULL

# rezeroing times by trial, by participants

@@

min(tmp.df3$timerezero, na.rm = TRUE)
max(tmp.df3$timerezero, na.rm = TRUE) # max shoudl be around 120s for 2 mnutes
natest<-subset(tmp.df3, is.na(tmp.df3$ssid) == TRUE)

@@

writing for ledalab

@@

tmp.df3<- tmp.df3%>%
  arrange(ssid, tNo,time)
# gsr baseline wil be the 1 second before tial start
# gsr to microsiemnes 1/J3*100000

tmp.df3$gsr_ms <- 1/tmp.df3$gsr*100000
unique(tmp.df3$ssid)
max(tmp.df3$gsr_ms)
min(tmp.df3$gsr_ms)

# gsr for leda
colnames(tmp.df3)
db_GSR<- select(tmp.df3, c(3,  14, 17, 50, 49 ))
db_GSR$tNo<- NULL
colnames(db_GSR)

unique(db_GSR$Condition)

db_GSR$Condition2<- if_else(db_GSR$Condition == 'Rest', 'Rest', 'IAPS')
unique(db_GSR$Condition2)
db_GSR$split_column<- paste0(db_GSR$Condition2,paste(db_GSR$ssid))
unique(db_GSR$split_column)
  (sprintf("writing for ledlab"))

split_column<- unique(db_GSR$split_column)

split_gsr = split(db_GSR, list(db_GSR$split_column))

    for (ssid in names(split_gsr)) {
      write_tsv(split_gsr[[ssid]][,c("time","gsr_ms", "trigger")], paste0("gpgsr_", paste0(ssid),".txt"), col_names = FALSE)
    }

# baselining gsr
```{r}
# use ms to baseline
tmp.df3_backup<- tmp.df3

tmp.df3$gsr_bas<- if_else(tmp.df3$timerezero3 >= -3 & tmp.df3$timerezero3 < 0, tmp.df3$gsr_ms, NULL)
# true if baseline within window
tmp.df3$gsr_bastrue<- if_else(tmp.df3$timerezero3 >= -3 & tmp.df3$timerezero3 < 0, TRUE, FALSE)

# create baseline median
tmp.df3$gsr_bas_mean<- NULL

tmp.df3<- tmp.df3%>%
  arrange(ssid, tNo,time)%>%
  group_by(ssid, tNo, gsr_bastrue)%>%
  mutate(gsr_bas_median = median(gsr_bas))

# fill the baseline mean
tmp.df3<- tmp.df3%>%
  # arrange(time)%>%
  group_by(ssid, tNo)%>%
  fill(gsr_bas_median)

# fill up to complete
unique(tmp.df3$gsrv)

tmp.df3<- tmp.df3%>%
  # arrange(time)%>%
  group_by(ssid, tNo)%>%
  fill(gsr_bas_median, .direction = 'up')

# do baseline correction
# 
tmp.df3<- tmp.df3%>%
  # arrange(time)%>%
  group_by(ssid, tNo)%>%
  mutate(gsr_basCor = gsr_ms - gsr_bas_median)

# rest baselining
tmp.df3<- tmp.df3%>%
  # arrange(time)%>%
  group_by(ssid, Condition)%>%
  mutate(gsr_restmedian = median(gsr_ms))

tmp.df3$gsr_basCor<- if_else(tmp.df3$Condition == 'Rest', tmp.df3$gsr_ms- tmp.df3$gsr_restmedian, tmp.df3$gsr_basCor)

# plot diagnosis
ggplot(subset(tmp.df3, tmp.df3$Condition == 'IAPS') , aes(x = timerezero3, y= gsr_basCor, colour = as.factor(ssid)))+
  # stat_summary(geom = 'line', fun.data = 'mean')+
    geom_smooth()+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

 ggplot(subset(tmp.df3, tmp.df3$Condition == 'Rest') , aes(x = timerezero3, y= gsr_basCor, colour = as.factor(ssid)))+
  # stat_summary(geom = 'line', fun.data = 'mean')+
    geom_smooth()+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2) 
  # tmp.df_norest$tNo<- as.factor(tmp.df_norest$tNo)

ggplot(subset(tmp.df3, tmp.df3$screencontent == 'stim') , aes(x = timerezero3, y= gsr_basCor, olour = as.factor(ssid)))+
    geom_smooth(aes())+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

tmp.df3_backup<- tmp.df3
# gsr respone
tmp.df3$gsr_resp_Log<- if_else(tmp.df3$timerezero3 > 1,TRUE, FALSE)
unique(tmp.df3$gsr_resp_Log)

tmp.df3 <- tmp.df3 %>%
    group_by(ssid, tNo, gsr_resp_Log )%>%
    mutate(gsr_response =   max(gsr_basCor))

# gsr response for every bit
unique(tmp.df3$screencontent)

tmp.df3<- tmp.df3%>%
  # arrange(time)%>%
  group_by(ssid, tNo, screencontent)%>%
  mutate(gsr_response_scrcont =   max(gsr_basCor))

tmp.df3$gsr_response <- if_else(tmp.df3$gsr_resp_Log == TRUE, tmp.df3$gsr_response, NULL)

tmp.df3<-
  tmp.df3%>%
  arrange(ssid, tNo,time)%>%
  group_by(ssid, tNo)%>%
    fill(gsr_response)

tmp.df3<-
  tmp.df3%>%
  arrange(ssid, tNo,time)%>%
  group_by(ssid, tNo)%>%
    fill(gsr_response,  .direction = c('up'))

unique(tmp.df3$gsr_response )

tmp.df3_backup<- tmp.df3
```

#baseline and clean pupil

```{r}
library(gazer)

min(tmp.df3$pupil, na.rm = TRUE)
max(tmp.df3$pupil, na.rm = TRUE)

tmp.df3$pupil<- if_else(tmp.df3$pupil> 7.2, tmp.df3$pupil, NULL)

tmp.df3$pupil<- if_else(tmp.df3$pupil< 45, tmp.df3$pupil, NULL)

tmp.df3_backup <- tmp.df3

# note that smothing and interpolating is order dependednt so order by ssid, trial and time
tmp.df3<- tmp.df3 %>%
  arrange(ssid, trialUnq,tNo, time)%>%
  group_by(ssid, trialUnq,tNo,screencontent) %>%
  mutate(extendpupil=gazer::extend_blinks(pupil, fillback=100, fillforward=100, hz=150))

min(tmp.df3$extendpupil, na.rm = TRUE)
max(tmp.df3$pupil, na.rm = TRUE)

# let's check

ggplot(subset(tmp.df3, tmp.df3$tNo == 3), aes(x = timerezero3, y= extendpupil , colour = as.factor(ssid)))+
      geom_line()
  # geom_line(aes(y = extendpupil), linetype = 'dashed', colour = 'red')

# Smooth and Interpolate
tmp.df3$subject<- tmp.df3$ssid
tmp.df3$trial = tmp.df3$trialUnq

# min(pup_extend$pupil, na.rm = TRUE)
tmp.df3$extendpupil
# ?smooth_interpolate_pupil

# library(gazer)

?smooth_interpolate_pupil

# vert order dependent
tmp.df3 <- smooth_interpolate_pupil(tmp.df3, pupil="pupil", extendpupil="extendpupil",
                                    extendblinks=TRUE, step.first= 'smooth',
                                    maxgap=Inf, 
                                    filter = 'moving',
                                    type="linear", hz=150, n = 30)

# tmp.df3<- tmp.df3 %>%
#   group_by(ssid, trialUnq,tNo,screencontent) %>%
#   smooth_interpolate_pupil(pupil="pupil", extendpupil="extendpupil",
#                                     extendblinks=TRUE, 
#                            step.first= 'smooth',
#                                     maxgap=10, 
#                                     filter = 'moving',
#                                     type="linear", hz=20, n = 10)
# 
# 
# tmp.df3<-
#   tmp.df3%>%
#   arrange(ssid,tNo,time)
#   # group_by(ssid, tNo, timerezero3)%>%
# 
# tmp.df3te<- tmp.df3 %>%
#   group_by(ssid, Condition,tNo,screencontent) %>%
#   smooth_interpolate_pupil(pupil="pupil", extendpupil="extendpupil",
#                                     extendblinks=TRUE, 
#                            step.first= 'smooth',
#                                     maxgap=Inf, 
#                                     filter = 'moving',
#                                     type="linear", hz=100, n = 5)

min(tmp.df3$pup_interp, na.rm = TRUE)
max(tmp.df3$pup_interp, na.rm = TRUE)

subset(tmp.df3, tNo == 20 & ssid == 347)%>%
ggplot(aes(x = timerezero3, y= pup_interp))+
  geom_line()+
   geom_line(aes(y = extendpupil), color = 'red')+
  geom_line(aes(y = pupil), colour = 'gray')
  # facet_grid(~Condition)

subset(tmp.df3, tNo == -7 & ssid == 350)%>%
ggplot(aes(x = timerezero3, y= pupil))+
  geom_line()

subset(tmp.df3, tNo == 1)%>%
ggplot(aes(x = timerezero3, y= pup_interp))+
  geom_line()+
   geom_line(aes(y = extendpupil), color = 'red')+
  # geom_line(aes(y = pup_interp), colour = 'gray')+
    facet_grid(~ssid)
  # facet_grid(~Condition)
```

# create baseline pupil mean
```{r}
tmp.df3backup<- tmp.df3
tmp.df3$pup_bas<- if_else(tmp.df3$timerezero3 >= -1 & tmp.df3$timerezero3 < 1, tmp.df3$pup_interp, NULL)
# true if bseline if baseline within widnown
tmp.df3$pup_bastrue<- if_else(tmp.df3$timerezero3 >= -1 & tmp.df3$timerezero3 < 1, TRUE, FALSE)

tmp.df3<- tmp.df3%>%
  # arrange(time)%>%
  group_by(ssid, tNo, pup_bastrue)%>%
  mutate(pup_bas_med = median(pup_bas))

# fill the baseline mean pupil
tmp.df3<- tmp.df3%>%
  # arrange(time)%>%
  group_by(ssid,tNo)%>%
  fill(pup_bas_med)

# fill up to complete pupil
tmp.df3<- tmp.df3%>%
  # arrange(time)%>%
  group_by(ssid, tNo)%>%
  fill(pup_bas_med, .direction = 'up')

# do baseline correction
tmp.df3<- tmp.df3%>%
  arrange(ssid, tNo, time)%>% # pay attentipn to order
  group_by(ssid, tNo)%>%
  mutate(pup_basCor = pup_interp - pup_bas_med)

# we only one the median for rest
tmp.df3<- tmp.df3%>%
  group_by(Condition)%>%
  mutate(pupilrest = median(pup_interp))

tmp.df3$pup_basCor<- if_else(tmp.df3$Condition == 'Rest', tmp.df3$pup_interp-tmp.df3$pupilrest, tmp.df3$pup_basCor)

# MAD removal
library(gazer)
max_pup<-tmp.df3 %>%
  dplyr::group_by(subject, trial) %>%
  dplyr::mutate(speed=speed_pupil(pup_interp,time)) %>%
  dplyr::mutate(MAD=calc_mad(speed))
  # dplyr::filter(speed < MAD)

tmp.df3<- max_pup

# instead of deleting, nus put NA
tmp.df3$pup_basCor<- if_else(tmp.df3$speed< tmp.df3$MAD, tmp.df3$pup_basCor, NULL)

tmp.df3$pup_interp_mad<- if_else(tmp.df3$speed< tmp.df3$MAD, tmp.df3$pup_interp, NULL)
# tmp.df3$pup_basCor<- if_else(tmp.df3$speed< tmp.df3$MAD, tmp.df3$pup_basCor, NULL)

ggplot(subset(tmp.df3, tNo == 10 & tmp.df3$ssid == 354) , aes(x = timerezero3, y= pup_basCor))+
    # geom_smooth(se = F)+
  geom_line()+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)
```
unique(tmp.df3$ssid)

```{r}
ggplot(subset(tmp.df3, tmp.df3$Condition == 'Rest') , aes(x = timerezero3, y= pup_basCor, colour = as.factor(ssid)))+
    geom_smooth(se = T)+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

```{r}
colnames(tmp.df3)
table(is.na(tmp.df3$gsr_ms))
table(is.na(tmp.df3$hr))

# heart rate

min(tmp.df3$hr, na.rm = TRUE)
max(tmp.df3$hr, na.rm = TRUE)

tmp.df3$hrv<- as.double(tmp.df3$hrv)
tmp.df3$hrv2<- if_else(is.na(tmp.df3$hrv) == TRUE, 999,tmp.df3$hrv)

tmp.df3$hr_clean<- tmp.df3$hr
tmp.df3$hr_clean<- as.double(tmp.df3$hr_clean)

tmp.df3$hr_clean<- if_else(tmp.df3$hrv2 >0,  tmp.df3$hr_clean, NULL)

tmp.df3$hr_clean<- if_else(tmp.df3$hr_clean > 40 & tmp.df3$hr_clean< 120, tmp.df3$hr_clean, NULL)

table(is.na(tmp.df3$hr_clean))
# interpolate, only 2 seconds 
library(zoo)

tmp.df3<- tmp.df3%>%
  arrange(ssid,tNo, time)

# tmp.df3$hr_interp =

tmp.df3<- tmp.df3%>%
  # arrange(ssid, time, tNo)%>%
  group_by(ssid, tNo,screencontent)%>%
  mutate(hr_interp = na.approx(hr_clean, na.rm=FALSE, maxgap =400))

  min(tmp.df3$hr, na.rm = TRUE)
ggplot(subset(tmp.df3, tmp.df3$tNo == -7 & tmp.df3$ssid == 352) , aes(x = timerezero3, y= hr_interp))+
    # geom_smooth(se = F)+
  geom_line()+
  geom_line(aes(y = hr_clean), linetype = 'dashed', colour = 'green', size = 0.3)+
   geom_line(aes(y = hr), linetype = 'dotted', colour = 'blue', size = 0.4)
    # geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    # geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    # geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    # geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

# na.approx(object, x = index(object), xout, ..., na.rm = TRUE, maxgap = Inf, along)
# z <- na.spline(zoo(y, x), maxgap = 2)

```{r}
tmp.df3 <- tmp.df3 %>%
    group_by(ssid, tNo, gsr_resp_Log, screencontent)%>%
    mutate(gsr_response_bycond =   max(gsr_basCor))

# tmp.df3$gsr_response_bycond <- if_else(tmp.df3$gsr_resp_Log == TRUE, tmp.df3$gsr_response, NULL)

colnames(tmp.df3)
# tmp.df4<- select(tmp.df3, c(1:3,10:22,27:30,33:37,44,46,47,51,53:56,60))

tmp.df4<- select(tmp.df3, c("session_id", "event_id", "ssid", "subject", "text", "trial","trialUnq", "tNo","trigger", "Condition" ,"screencontent","stim",
                            "time", "timerezero", "timerezero2", "timerezero3", "status","filename",
                            "left_gaze_x_cor_pix","right_gaze_x_cor_pix","left_gaze_y_cor_pix","right_gaze_y_cor_pix",  "gaze_x_cor_pix",  "gaze_y_cor_pix",
                            "pupil", "pup_interp_mad", "extendpupil","pup_basCor",
                            "hr", "hrv", "hrp", "hr_clean", 'hr_interp', 
                            'gsr_ms', 'gsr_basCor', 'gsr_response', 'gsr_response_bycond', 
                            "distance"))
head(tmp.df4)

# calculate trackloss
unique(tmp.df4$status)

tmp.df4$trackloss<- if_else(is.na(tmp.df4$gaze_x_cor_pix) == TRUE, 0, 
                         if_else(is.na(tmp.df4$gaze_y_cor_pix) == TRUE, 0, 1))
unique(tmp.df4$trackloss)

# tmp.df4$trackloss<- if_else(tmp.df4$status> 0, 1, 0)

tmp.df4$hr_trackloss<- if_else(is.na(tmp.df4$hr_clean) == TRUE, 0, 1) # 1 means valid, 0 missing

tmp.df4 <- tmp.df4%>%
  group_by(ssid, tNo, trialUnq, text)%>%
  mutate(gaze_valid_prop = sum(trackloss)/n())%>%
  mutate(gaze_loss_prop = 1 - gaze_valid_prop)%>%
  mutate(hr_valid_prop = sum(hr_trackloss)/n())%>%
  mutate(hr_loss_prop = 1 - hr_valid_prop)

# check to see this is right
ggplot(subset(tmp.df4, tmp.df3$ssid == 353) , aes(x = tNo, y= hr_valid_prop))+
    # geom_smooth(se = F)+
  geom_line()+
  geom_line(aes(y = hr_loss_prop), linetype = 'dashed', colour = 'green', size = 0.3)
   # geom_line(aes(y = hr), linetype = 'dotted', colour = 'blue', size = 0.4)

ggplot(subset(tmp.df4, tmp.df3$ssid == 354) , aes(x = tNo, y= gaze_valid_prop))+
    # geom_smooth(se = F)+
  geom_line()+
  geom_line(aes(y = gaze_loss_prop), linetype = 'dashed', colour = 'green', size = 0.3)
   # geom_line(aes(y = hr), linetype = 'dotted', colour = 'blue', size = 0.4)

colnames(tmp.df4)
write_csv(tmp.df4, 'interodata_clean_gp.csv')

# tmp.df4<- read_csv('intero_tsdata_clean.csv')

tmp.df4<- tmp.df4%>%
  arrange(ssid, time, tNo)

unique(tmp.df4$trigger)

# why

tmp.df4$trigger2<- tmp.df4$trigger

tmp.df4$trigger2<- if_else(tmp.df4$trigger>99, tmp.df4$trigger, as.double(tmp.df4$tNo))

unique(tmp.df4$trigger2)

# \why?
tmp.df4<- tmp.df4%>%
  group_by(ssid, tNo, text)%>%
  mutate(stdev_gaze_x = sd(gaze_x_cor_pix, na.rm = TRUE))%>%
  mutate(stdev_gaze_y = sd(gaze_y_cor_pix, na.rm = TRUE))

tmp.df4$sdev_gazesum<- tmp.df4$stdev_gaze_x+ tmp.df4$stdev_gaze_y

# summarise
tmp.df4_sum<- tmp.df4%>%
  arrange(ssid, time, tNo)%>%
  group_by(ssid, subject, trial, Condition, screencontent, tNo, stim, trialUnq,text)%>%
  summarise_at(c('pup_basCor', 'gsr_response','gsr_response_bycond', 'gsr_basCor', 'hr_interp', 'hr_clean', 'time', 'gaze_loss_prop', 'gaze_valid_prop', 'hr_valid_prop', 'hr_loss_prop', 'timerezero3', 'sdev_gazesum', 'stdev_gaze_x', 'stdev_gaze_y'), mean, na.rm = TRUE)

tmp.df4_sum$trigger<-if_else(tmp.df4_sum$screencontent == 'fixation', 100,
                          if_else(tmp.df4_sum$screencontent == 'ValenceResp', 101,
                             if_else(tmp.df4_sum$screencontent == 'IntResp', 102, as.double(tmp.df4_sum$tNo))))

unique(tmp.df4_sum$trigger)

unique(tmp.df4_sum$trigger)
tmp.df4_sum<- tmp.df4_sum%>%
  arrange(time, tNo, ssid)

write_csv(tmp.df4_sum, 'intero_aggdata_clean.csv')

write_csv(tmp.df4_sum, 'intero_aggdata_clean_3046_355.csv')
# 
# head(tmp.df4_sum)
# unique(tmp.df4_sum$tNo)

ggplot(tmp.df4_sum, aes(tNo, gaze_valid_prop, colour = as.factor(ssid)))+
  geom_point()+
  geom_line()

ggplot(subset(tmp.df4_sum, tmp.df4_sum$screencontent == 'stim'), aes(tNo, gaze_valid_prop, colour = as.factor(ssid)))+
  geom_point()+
  geom_line()

ggplot(subset(tmp.df4_sum, tmp.df4_sum$screencontent == 'stim'), aes(gaze_valid_prop, colour = as.factor(ssid)))+
# geom_density()+
  geom_histogram()
  # geom_line()

# for gaze parsing

@@

(sprintf("preparing for gazepath"))

colnames(tmp.df4)

  for_gazepath<- select(tmp.df4, c(2:15,17:26, 39:40,42:43))

  for_gazepath$screencontent[for_gazepath$screencontent == 'rest1']<- 'fixation'
  for_gazepath<- for_gazepath%>%
    arrange(ssid, time, tNo)

  colnames(for_gazepath)

  for_gazepath<- subset(for_gazepath, is.na(for_gazepath$time) == FALSE)
   # View(for_gazepath)

  for_gazepath$split_column<- paste0(for_gazepath$ssid, paste0(for_gazepath$screencontent))
  splitcol<- unique(for_gazepath$split_column)
  splitcol
  # ssid<- unique(for_gazepath$ssid)
  # ssid
  split_df = split(for_gazepath, list(for_gazepath$split_column))

  (sprintf("writing for gazepath"))
  # ssid = split(for_gazepath, list(for_gazepath$ssid))
  # for (ssid in names(split_df)) {
    for (splitcol in names(split_df)) {
      # message( split_df[splitcol])
      write_csv(split_df[[splitcol]], paste0('gp_',paste0(splitcol),".csv"))
    }

```
process gazepath and ledalab
```{r}
library(gazepath)
GUI()

@@

# Import Ledalab
Ledalab('/Users/heliocuve/Documents/InteroStudy/EATProcesing/EAT/forLeda/', 'open','text3','downsample', 15, 'smooth',{'adapt'}, 'analyze','CDA', 'optimize',3, 'export_era', [1 105 .01 2])
```{r}
read_leda <- function(flnm) {
  data.table::fread(flnm) %>% 
    mutate(filename = flnm)
}

# now read them
db_leda <-
  list.files(pattern = "*.txt", 
             full.names = T) %>% 
  map_df(~read_leda(.))

db_leda$trigger<- as.numeric(db_leda$Event.NID)
unique(db_leda$trigger)
db_leda$ssid<- as.numeric(substr(db_leda$filename, 13,15))
colnames(tmp.df4_sum)
colnames(db_leda)
nrow(tmp.df4_sum)
nrow(db_leda)
colnames(tmp.df4_sum)
tmp.df4_sum2<- subset(tmp.df4_sum,tmp.df4_sum$tNo != -7)
tmp.df4_sum2<- tmp.df4_sum2%>%
  arrange(ssid, time, tNo)%>%
  group_by(ssid)%>%
  mutate(order = 1:224)

db_leda2<- subset(db_leda, db_leda$trigger != -7)
db_leda2<- db_leda2%>%
  arrange(ssid, Event.Nr)%>%
  group_by(ssid)%>%
  mutate(order = 1:224)

tmp.df4_sum_fullt<- left_join(tmp.df4_sum2, db_leda2, by = c("order", "trigger", "ssid"))
tmp.df4_sum_full_backup<- tmp.df4_sum_full

tmp.df4_sum_full<- left_join(tmp.df4_sum2, db_leda2, by = c("order", "trigger", "ssid"))

# tmp.df4_sum_full<- bind_cols(tmp.df4_sum, db_leda)

tmp.df4_sum_full<- tmp.df4_sum_full%>%
  arrange(ssid, tNo)
```

read parsed data
```{r}
read_parsed <- function(flnm) {
    read_csv(flnm) %>%
        mutate(filename = flnm)
}

db_parsed <- list.files(pattern = "*.csv", 
               full.names = T) %>% 
    map_df(~read_parsed(.))

# return content between spaces
# pu things in the correct order
# library(stringr)
db_parsed$screencontent<- str_extract(db_parsed$trialUnq, "(?<=\\s)(.*)(?=\\s)")
unique(db_parsed$screencontent)
db_parsed$screencontent[db_parsed$screencontent == 'rest1']<- 'fixation'

db_parsed$screencontent_no<- if_else(db_parsed$screencontent == 'fixation', 1,
                                      if_else(db_parsed$screencontent == 'stim', 2,
                                              if_else(db_parsed$screencontent == 'ValenceResp', 3,
                                                      if_else(db_parsed$screencontent == 'IntResp', 4, NULL))))

db_parsed$tNo<- as.numeric(substr(db_parsed$trialUnq, 1,2))
unique(db_parsed$screencontent_no)
db_parsed$ssid<- substr(db_parsed$Participant, 4,6)

db_parsed<- db_parsed%>%
  arrange(ssid, tNo, screencontent_no)

ggplot(db_parsed, aes(mean_x, mean_y))+
  geom_point()+
  facet_grid(ssid~screencontent)

unique(db_parsed$tNo)
# db_parsed$tNo<- if_else(db_parsed$tNo > -1, db_parsed$tNo-1, db_parsed$tNo )

db_parsed<-db_parsed%>%
  group_by(ssid, tNo, screencontent,Value)%>%
  mutate(mean_fix_dur = mean(Duration))%>%
  mutate(mean_POGsdSacAmp = mean(POGsdSacAmp))%>%
  mutate(fix_count = sum(Value == 'f'))%>%
  mutate(sac_count = sum(Value == 's'))

# this might be needed for tempoal analisys
write_csv(db_parsed, 'db_parsed.csv')

db_parsed_summarised<- db_parsed%>%
  group_by(ssid, tNo,screencontent, trialUnq, screencontent_no, Value)%>%
  summarise_at(c('fix_count', 'sac_count', 'mean_fix_dur', 'mean_POGsdSacAmp', 'RMS'), mean, na.rm = TRUE)

colnames(db_parsed_summarised)
db_parsed_summarised_fix<- subset(db_parsed_summarised, db_parsed_summarised$Value == 'f')
db_parsed_summarised_fix$sac_count<- NULL
db_parsed_summarised_fix$POGsd<- db_parsed_summarised_fix$mean_POGsdSacAmp
db_parsed_summarised_fix$mean_POGsdSacAmp<- NULL
db_parsed_summarised_fix$Value<-NULL
db_parsed_summarised_sac<- subset(db_parsed_summarised, db_parsed_summarised$Value == 's')
db_parsed_summarised_sac$fix_count<- NULL
db_parsed_summarised_sac$mean_sac_dur<-  db_parsed_summarised_sac$mean_fix_dur
db_parsed_summarised_sac$SacAmp<- db_parsed_summarised_sac$mean_POGsdSacAmp
db_parsed_summarised_sac$mean_POGsdSacAmp<- NULL
db_parsed_summarised_sac$mean_fix_dur<- NULL
db_parsed_summarised_sac$RMS<- NULL
db_parsed_summarised_sac$Value<- NULL
View(db_parsed_summarised_sac)
View(db_parsed_summarised_fix)
db_parsed_summarised_sac$Value<- NULL
db_parsed_summarised_fix$Value<- NULL
db_parsed_summarised_sac$RMS<- NULL

View(db_parsed)

colnames(db_parsed_summarised_fix)
colnames(db_parsed_summarised_sac)

db_parsed_summarised2<- left_join(db_parsed_summarised_fix,db_parsed_summarised_sac, by = (c('ssid', 'tNo', 'screencontent', "screencontent_no", "trialUnq")))

db_parsed_summarised2<- db_parsed_summarised2%>%
  arrange(ssid, tNo, screencontent_no)
# View(db_parsed_summarised2)
write_csv(db_parsed_summarised2, 'db_parsed_summarised.csv')
